Analysing intention of chatbots use after COVID pandemic using Machine Learning

### 2023-01-07 edubots_surveys_future_paper.Rnw
explaining what each author have done

This work has been supported by EDUBOTS project, funded under the scheme Erasmus + KA2: Cooperation for innovation and the exchange of good practices - Knowledge Alliances (grant agreement no: 612446).

@@

All the authors have contributed to the study presented in this manuscript. 
JJM has been the leader, drafted the first versions of the survey and supervised the writing of the manuscript.
PAC has...
AMM has ...
FB has...
NA has...
OT has...
AG has...
All authors have read and approved the final manuscript.

>>>>

This work has been supported by EDUBOTS project, funded under the scheme Erasmus + KA2: Cooperation for innovation and the exchange of good practices - Knowledge Alliances (grant agreement no: 612446).
It has also been supported by DemocratAI::UGR project (PID2020-115570GB-C22).

@@

All the authors have contributed to the study presented in this manuscript. 
JJM has been the leader, drafted the first versions of the survey and supervised the writing of the manuscript; 
AMM, FB, PAC, NA, OT, AG have done editing, writing and proofreading tasks.
All authors have read and approved the final manuscript.
